---
title: 'Chapter 2: Data Structures'
author: "Emeka Mbazor"
date: "3/23/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Vector Exercises

1. What are the six types of atomic vector? How does a list differ from an atomic vector?

The six types of atomic vectors are:
  * logical
  * integer
  * double
  * character
  * complex
  * real
  
An atomic vector can only contain elements of a single type while a list can contain elements of any type (including lists themselves).

2. What makes `is.vector()` and `is.numeric()` fundamentally different to `is.list()` and `is.character()`?

`is.vector()` returns true if the object is an atomic vector or a list and `is.numeric` returns true if the object is an integer vector or a double vector. But `is.list()` only returns true if the object is a list and `is.character()` only returns true if the object is a character vector.

3. Test your knowledge of vector coercion rules by predicting the output of the following uses of c():

```{r}
c(1, FALSE)
c("a", 1)
c(list(1), "a")
c(TRUE, 1L)
```

```
[1, 0]
["a", "1"]
[ {1}, {"a"}]
[1, 1]
```

4. Why do you need to use `unlist()` to convert a list to an atomic vector? Why doesn’t `as.vector()` work?

`as.vector()` doesn't convert a list to an atomic vector because a list is already a vector. 

5. Why is `1 == "1"` true? Why is `-1 < FALSE` true? Why is `"one" < 2` false?

`1 == "1"` is true because 1 is converted into the character `"1"` and "1" is equal to itself. `-1 < FALSE` is true because `FALSE` is converted into the integer `0` and -1 is less than 0. `"one" < 2` is false because 2 is converted into the character `"2"` and 2 comes before "o" on the ASCII table.

6. Why is the default missing value, `NA`, a logical vector? What’s special about logical vectors? (Hint: think about `c(FALSE, NA_character_)`.)

`NA` is a logical vector because logical vectors are the most flexible. 




