---
title: 'Chapter 2: Names and Values'
author: "Emeka Mbazor"
date: "4/1/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the prerequisite libraries. 

```{r}
library(lobstr)
library(tidyverse)
```

## 2.2.2 Exercises 

1. Explain the relationship between `a`, `b`, `c` and `d` in the following code:

```{r}
a <- 1:10
b <- a
c <- b
d <- 1:10

obj_addr(a)
obj_addr(b)
obj_addr(c)
obj_addr(d)
```

There are two objects that are both vectors containing numbers from 1 to 10 (inclusive). `a`, `b`, and `c` refer to the first object and `d` refer to the second object. 

2. The following code accesses the mean function in multiple ways. Do they all point to the same underlying function object? Verify this with lobstr::obj_addr().

```
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```

They all point to the same underlyign function object because they all have the same object addresses.

```{r}
mean %>% obj_addr()
base::mean %>% obj_addr()
get("mean") %>% obj_addr()
evalq(mean) %>% obj_addr()
match.fun("mean") %>% obj_addr()
```




