---
title: 'Chapter 2: Names and Values'
author: "Emeka Mbazor"
date: "4/1/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load the prerequisite libraries. 

```{r}
library(lobstr)
library(tidyverse)
```

## 2.2.2 Exercises 

1. Explain the relationship between `a`, `b`, `c` and `d` in the following code:

```{r}
a <- 1:10
b <- a
c <- b
d <- 1:10

obj_addr(a)
obj_addr(b)
obj_addr(c)
obj_addr(d)
```

There are two objects that are both vectors containing numbers from 1 to 10 (inclusive). `a`, `b`, and `c` refer to the first object and `d` refer to the second object. 

2. The following code accesses the mean function in multiple ways. Do they all point to the same underlying function object? Verify this with lobstr::obj_addr().

```
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```

They all point to the same underlyign function object because they all have the same object addresses.

```{r}
mean %>% obj_addr()
base::mean %>% obj_addr()
get("mean") %>% obj_addr()
evalq(mean) %>% obj_addr()
match.fun("mean") %>% obj_addr()
```

3. By default, base R data import functions, like `read.csv()`, will automatically convert non-syntactic names to syntactic ones. Why might this be problematic? What option allows you to suppress this behaviour?

This might be problematic because it might lead to a loss of information in column names. This behavior can be supressed by setting the parameter `check.names` to `FALSE`.

4. What rules does `make.names()` use to convert non-syntactic names into syntactic ones?

`make.names()` prepends the "X" character to the name if the first character isn't a letter. Invalid characters are translated to "." Missing values are translated to the characters "NA". Names that match existing R keywords have a dot appended to them. 

5. I slightly simplified the rules that govern syntactic names. Why is `.123e1` not a syntactic name? Read ?make.names for the full details.

```{r}
make.names(".123e1")
```

`.123e1` is not a syntactic name because it doesn't begin with a letter.

## 2.3.6 Exercises

1. Why is `tracemem(1:10)` not useful?

`tracemem(1:10)` is not useful because there's no way to make a copy of a vector without an initial reference to that vector.

2. Explain why `tracemem()` shows two copies when you run this code. Hint: carefully look at the difference between this code and the code shown earlier in the section.

```{r}
x <- c(1L, 2L, 3L)
tracemem(x)

x[[3]] <- 4

untracemem(x)

x<- c(1L, 2L, 3L)
tracemem(x)
x[[3]] <- 4L
```

`tracemem()` shows two copies when you run this code first the integer vector is coerced into a double vector and then the third number is replaced by '4'.

3. Sketch out the relationship between the following objects:

```{r}
a <- 1:10
b <- list(a, a)
c <- list(b, a, 1:10)

ref(c)
```



