---
title: 'Chapter 3: Subsetting'
author: "Emeka Mbazor"
date: "3/23/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Types Exercises

1. Fix each of the following common data frame subsetting errors:

```
mtcars[mtcars$cyl = 4, ]
mtcars[-1:4, ]
mtcars[mtcars$cyl <= 5]
mtcars[mtcars$cyl == 4 | 6, ]
```

```{r}
mtcars[mtcars$cyl == 4, ]
mtcars[2:4, ]
mtcars[mtcars$cyl <= 5, ]
mtcars[(mtcars$cyl == 4 | mtcars$cyl == 6), ]
```

2. Why does `x <- 1:5; x[NA]` yield five missing values? (Hint: why is it different from `x[NA_real_]`?)

```{r}
x <- 1:5
x[NA]
x[NA_real_]
```

`x <- 1:5; x[NA]` yields five missing values because since `NA` is a logical vector it gets recycled four times. 

3. What does `upper.tri()` return? How does subsetting a matrix with it work? 

```
x <- outer(1:5, 1:5, FUN = "*")
x[upper.tri(x)]
```

```{r}
x <- outer(1:5, 1:5, FUN = "*")
x
x[upper.tri(x)]
```

`upper.tri()` returns a logical matrix with the positions in the upper triangluar half of the matrix being marked `TRUE` and the lower triangular half of the matrix marked `FALSE`. Subsetting a matrix with it returns only the values in upper triagular half.

4. Why does `mtcars[1:20]` return an error? How does it differ from the similar `mtcars[1:20, ]`?

```{r}
str(mtcars)
#mtcars[1:20]
mtcars[1:11]
mtcars[1:20, ]
```

`mtcars[1:20]` returns an error because when you use a single dimension to subset a 2D object, you're subsetting that object's columns and `mtcars` only have 11 columns. 

`mtcars[1:20, ]` is different because it's subsetting row-wise instead of column-wise.


5. Implement your own function that extracts the diagonal entries form a matrix. (it shoudld behave like `diag(x)` where x is matrix).

```{r}
x <- matrix(1:16, ncol = 4, nrow = 4)
x
diag(x)

y <- matrix(1:15, ncol = 3, nrow = 5)
y
diag(y)

diag2 <- function(x) {
  
  if(nrow(x) < ncol(x)) {
    limit <- nrow(x)
  } else {
    limit <- ncol(x)
  }
  
  y <- rep(0, limit)
  
  for(i in 1:limit) {
    y[i] <- x[i, i] 
  }
  
  return(y)
}

diag2(x)

diag2(y)
```

6. What does `df[is.na(df)] <- 0` do? How does it work?

It replaces all `NA` values with 0. This is because `is.na()` returns a data frame filled with logical values based on the presence of a missing value or not. 

