---
title: 'Chapter 3: Subsetting'
author: "Emeka Mbazor"
date: "3/23/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Types Exercises

1. Fix each of the following common data frame subsetting errors:

```
mtcars[mtcars$cyl = 4, ]
mtcars[-1:4, ]
mtcars[mtcars$cyl <= 5]
mtcars[mtcars$cyl == 4 | 6, ]
```

```{r}
mtcars[mtcars$cyl == 4, ]
mtcars[2:4, ]
mtcars[mtcars$cyl <= 5, ]
mtcars[(mtcars$cyl == 4 | mtcars$cyl == 6), ]
```

2. Why does `x <- 1:5; x[NA]` yield five missing values? (Hint: why is it different from `x[NA_real_]`?)

```{r}
x <- 1:5
x[NA]
x[NA_real_]
```

`x <- 1:5; x[NA]` yields five missing values because since `NA` is a logical vector it gets recycled four times. 

3. What does `upper.tri()` return? How does subsetting a matrix with it work? 

```
x <- outer(1:5, 1:5, FUN = "*")
x[upper.tri(x)]
```

```{r}
x <- outer(1:5, 1:5, FUN = "*")
x
x[upper.tri(x)]
```

`upper.tri()` returns a logical matrix with the positions in the upper triangluar half of the matrix being marked `TRUE` and the lower triangular half of the matrix marked `FALSE`. Subsetting a matrix with it returns only the values in upper triagular half.






