---
title: 'Chapter 5: Control Flow'
author: "Emeka Mbazor"
date: "4/2/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 5.2.4 Exercises

1. What type of vector does each of the following calls to `ifelse()` return?

```{r}
ifelse(TRUE, 1, "no")
ifelse(FALSE, 1, "no")
ifelse(NA, 1, "no")
```

Read the documentation and write down the rules in your own words.

`ifelse()` evaluates the logical expression that is the first parameter. If the logical expression evaluates to `TRUE`, the function returns the second argument. If the logical expression evaluates to `FALSE`, the function returns the third argument. If the logical expression is a missing value, the function returns a missing value. 

2. Why does the following code work?

```{r}
x <- 1:10
str(length(x))
if (length(x)) "not empty" else "empty"


x <- numeric()
str(x)
if (length(x)) "not empty" else "empty"
```

The code works because `if()` accepts integers and treats nonzero integers as `TRUE` and the rest as `FALSE`.

## 5.3.3 Exercises

1. Why does this code succeed without errors or warnings?

```{r}
x <- numeric()
out <- vector("list", length(x))
for (i in 1:length(x)) {
  out[i] <- x[i] ^ 2
}
out
```

This code succeeds without errors because `x` is a numeric vector of length 0 and `out` is a list of length 0. The `for` loop has two iterations since `i` counts down from 1 to 0. `x[1]` is `NA` because `NA ^ 2` results in `NA`. The second iteration doesn't do anything. This results with `out` being a list of length 1 with the only value being a missing one.

2. When the following code is evaluated, what can you say about the vector being iterated?

```{r}
xs <- c(1, 2, 3)
for(x in xs) {
  xs <- c(xs, x * 2)
}
xs
```

The vector being iterated is a seperate copy from the vector being altered within the `for` loop. 